Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-21 article_review/Manuscript.tex
Minor changes

The results are averaged over $100$ repetitions and compared in Table \ref{compa_MC}. The comparison is made based on the estimation errors and failures rates. The column \textit{precision} corresponds to the average width of the bootstrap confidence interval for the iid sampling method.

@@

{\color{purple} The precision of our procedure was also compared to a simpler method based on random sampling and straightforward confidence intervals. For an identical number of evaluations, our procedure was far more accurate than an iid sampling method. The origin of the discrepancy observed lies in the use of a more robust error bound.}

>>>>

The results are averaged over $100$ repetitions and compared in Table \ref{compa_MC}. The comparison is made based on the estimation errors and failures rates. The column \textit{precision} corresponds to the width of the bootstrap confidence interval for the iid sampling method.

@@

{\color{purple} The precision of our procedure was also compared to a simpler method based on iid sampling and straightforward confidence intervals. For an identical number of evaluations, our procedure was far more accurate than the iid sampling method. The origin of the discrepancy observed lies in the use of a more robust error bound.}
